%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------

  \cventry
    {\textbf{Master's Thesis Intern In Machine Learning}} % Job title
    {Electronic Arts, SEED} % Organisation
    {\textbf{Stockholm, Sweden}} % Location
    {\textbf{Jan 2024 - Current}} % Date(s)
    {
      \ifbool{FullVersion}{
        Currently working on my master's thesis as an intern in the SEED research team at Electronic Arts, researching the application of multi-agent reinforcement learning methods in game-AI - Under supervision of Linus Gisslén and Alessandro Sestini
      }{
        \begin{cvitems}
            \item {Currently working on my master's thesis as an intern in the SEED research team at Electronic Arts.}
            \item {Researching the application of modern \emph{multi-agent reinforcement learning} methods in game-AI using machine learning, in addition to possible improvements to the methods.}
        \end{cvitems}
      }
    }
    
  \cventry
    {\textbf{Unity Game Developer (Internship)}} % Job title
    {Medrick Games} % Organisation
    {\textbf{Tehran, Iran (Remote)}} % Location
    {\textbf{Sept 2021 - Aug 2022}} % Date(s)
    {
      \ifbool{FullVersion}{
        In September 2021, I got accepted for an internship position at Medrick Games, which is an active game publishing and development studio in Tehran, Iran. Working remotely from Shiraz during most of the internship period, I worked as an Unity game developer in the hyper-casual game development department. In addition to game development, I participated in game design tasks such as idea development and refinement. During this time, my team and I made \emph{four complete casual/hyper-casual mobile games} among other activities.
      }{
        \begin{cvitems}
            \item {Collaborated with my team to develop four casual/hyper-casual mobile games, among other project contributions.}
            \item {Primarily focused on programming game mechanics and gameplay for prototypes, utilizing Unity/C\#.}
            \item {Participated in game design tasks, including idea development and refinement. Additionally involved in marketing activities, such as producing one-minute promotional videos for our games.}
        \end{cvitems}
      }
    }

\end{cventries}
